Transient Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of Complex Quasiperiodic Variables from TESS

### 2023-08-20 paper/ms.tex
update ms
fix typo

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f5.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The
      light curve is binned to 15-minute intervals so that there are
      96 points per day, and each point is connected by a line.  Data
      gaps longer are not interpolated; if data are missing, nothing
      is plotted.  The red vertical lines highlight apparently
      instantaneous state changes in the shape of the dip pattern.  
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

In Section~\ref{subsec:binarity}, we found that a significant fraction
of the CQVs show indications of unresolved binarity.  Excess noise
above the Gaia single-source astrometric model is common
(\ngoodhighruwe/\ngoods\ high-quality CQVs with RUWE$_{\rm DR3}$$>$2),
as is the presence of multiple periods in the TESS light curves
(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
always accompanied by multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe high-quality CQVs).  The
latter point strongly corroborates the idea that most sources with
RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
projected apparent separations below 1$''$, and projected physical
separations $\lesssim$50\,AU.

>>>>

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.98\textwidth]{f5.pdf}
		\vspace{-0.3cm}
		\caption{
      {\bf LP 12-502 (TIC~402980664) light curve}, where each time
      chunk represents one TESS orbit.  Data were acquired in Sectors
      18-19, 25-26, 53, and 57-58.  Flares are drawn in gray.  The
      light curve is binned to 15-minute intervals so that there are
      96 points per day, and each point is connected by a line.  Data
      gaps are not interpolated; if data are missing, nothing
      is plotted.  The red vertical lines highlight apparently
      instantaneous state changes in the shape of the dip pattern.  
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

@@

In Section~\ref{subsec:binarity}, we found that a significant fraction
of the CQVs show indications of unresolved binarity.  Excess noise
above the Gaia single-source astrometric model is common
(\ngoodhighruwe/\ngoods\ high-quality CQVs with RUWE$_{\rm DR3}$$>$2),
as is the presence of multiple periods in the TESS light curves
(\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise is almost
always accompanied by multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CQVs).  The
latter point strongly corroborates the idea that most sources with
RUWE$_{\rm DR3}$$>$2 are intermediate separation binaries with
projected apparent separations below 1$''$, and projected physical
separations $\lesssim$50\,AU.
